Consistent Polyhedral Surrogates via Embedding

### 2021-04-07 notes/top-k.tex
Top k note

\begin{lemma}\label{lem:extra-elts-zero}
%  \raf{This statement seems off.  I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
	For all $u \in \reals^d$, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
\end{lemma}
\begin{proof}
	By Lemma~\ref{lem:invar-ones}, we can fix $u_{[k+1]} = 0$.
	We then have $u_{[i]} \leq 0$ for all $i \geq k+1$.
	Consider $u'$ such that $u'_{[i]} = u_{[i]}$ for all $i$ so that $u_{[i]} \geq 0$, and $u'_{[i]} = 0$ otherwise.
	Observe that $u$ and $u'$ have the same ordering on their elements.

@@

\section{Re-writing the loss}
The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:nonneg} and ~\ref{assum:top-threshold}.

@@

With Assumptions~\ref{assum:nonneg} and \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can now rewrite the loss for each outcome in a simplified form.
\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}\jessie{I'm not sure where?  I don't see it.}
\begin{lemma}\label{lem:new-form-surrogate}
	For $u \in \U \cap \U_{\pi(u)}$, the top-$k$ surrogate can be written:
\begin{align*} 
L^{top-k}(u)_y  &= 1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) = \begin{cases}
1 - u_y + \bar u - \frac{u_y}{k} & u_y \leq 1\\
1 - u_y + \bar u - \frac{1}{k} & u_y > 1
\end{cases}
~.~
\end{align*}
\end{lemma}
\begin{proof}
	First, consider
\begin{align*}
	L^{top-k}(u)_y &= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= 1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]}~,
	\end{align*}
	by Lemma~\ref{lem:get-rid-max-op}.

@@

Consider the following finite set.
\begin{align*}
\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
\end{align*}
Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$.

@@

First, fix a permutation $\pi$ on the elements of $\{1,2,\ldots, n\}$.
Consider $u \in \U \cap \U_\pi$ ordered by $\pi$.
Define the polytopes $P^\pi_a := \{u \in \U\cap \U_\pi : u_i \in [0,1] \text{ or } u_i > 1\}$, for some choice of inequality for each $i \in [n]$.
One can observe there are only a finite number of such polytopes as there are only finitely many permutations $\pi$ of $\{1,2,\ldots, n\}$.
Moreover, there are only finitely many ($2^n$) ways to assign $a_j = \{u_i \in \{[0,1], (1, \bar u_{-i} + 1]\} \}$ for all $i$, and therefore there are only finitely many polytopes.

>>>>

\begin{lemma}\label{lem:extra-elts-zero}
	For all $u \in \reals^d$, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
	\jessie{Claim: $R := \{u \in \reals^n_+ \mid \|u\|_0 \leq k\}$ is a representative set for $L^{top-k}$.}
\end{lemma}
\begin{proof}
	By Lemma~\ref{lem:invar-ones}, we can fix $u_{[k+1]} = 0$.
	We then have $u_{[i]} \leq 0$ for all $i \geq k+1$.
	Consider $u'$ such that $u'_{[i]} = u_{[i]}$ for all $i$ so that $u_{[i]} \geq 0$, and $u'_{[i]} = 0$ otherwise.
	Observe that $u$ and $u'$ have the same ordering on their elements.

@@

\section{Re-writing the loss}
The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:nonneg} and ~\ref{assum:top-threshold}.
\jessie{Can we claim $\U$ is a representative set for $L^{top-k}$?  Would take some more work.}

@@

With Assumptions~\ref{assum:nonneg} and \ref{assum:top-threshold} and Lemma~\ref{lem:get-rid-max-op}, we can now rewrite the loss for each outcome in a simplified form.
\raf{Note: some inconsistency in the way you use this $\min$ operator and denote $\ones$; see below too}\jessie{$\min$ is element-wise, but in this next instance, is just on scalars.}
\begin{lemma}\label{lem:new-form-surrogate}
	For $u \in \U \cap \U_{\pi(u)}$, the top-$k$ surrogate can be written:
\begin{align*} 
L^{top-k}(u)_y  &= 1 - u_y + \bar u - \frac{1}{k}(\min(u_y, 1)) = \begin{cases}
1 - u_y + \bar u - \frac{u_y}{k} & u_y \leq 1\\
1 - u_y + \bar u - \frac{1}{k} & u_y > 1
\end{cases}
~.~
\end{align*}
\end{lemma}
\begin{proof}
	First, consider
\begin{align*}
	L^{top-k}(u)_y &= \left(1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]} \right)_+\\
	&= 1 -u_y + \frac{1}{k} \sum_{i=1}^k ((u - e_y)_{[i]}~,
	\end{align*}
	by Lemma~\ref{lem:get-rid-max-op}.

@@

Consider the following finite set.
\begin{align*}
\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
\end{align*}
\jessie{Ultimately, WTS $\R$ is representative for $L^{top-k}$.}
Throughout, we consider $c(u) := \frac{|M(u)| + k -1}{k - |H(u)|}$, where $M(u) = \{i \in [n] : u_i \in [0,1] \}$ and $H(u) = \{i \in [n] : u_i > 1\}$.

@@

First, fix a permutation $\pi$ on the elements of $\{1,2,\ldots, n\}$.
Consider $u \in \U \cap \U_\pi$ ordered by $\pi$.
Define the polytopes $P^\pi_a := \{u \in \U\cap \U_\pi : u_i \in [0,1] \text{ or } u_i > 1\}$, for some choice of inequality for each $i \in [n]$.
One can observe there are only a finite number of such polytopes as there are only finitely many permutations $\pi$ of $\{1,2,\ldots, n\}$.
Moreover, there are only finitely many ($2^n$) ways to assign $a = \{u_i \in \{[0,1], (1, \bar u_{-i} + 1]\} \}$ for all $i$, and therefore there are only finitely many polytopes.
